Capstone Movielens Report

### 2025-01-30 reports/capstone-movielens-report.Rmd
Bib-files organized.

```{r setup, include=TRUE}
library(RefManageR)
bib <- ReadBib(system.file("Bib", "references.bib", 
                           package = "RefManageR"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

```{r setup, include=TRUE}
library(RefManageR)
bib <- ReadBib(system.file("Bib", "biblatexExamples.bib", 
                           package = "RefManageR"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
knitr::opts_chunk$set(echo = TRUE)
```
